lnc34a splice junctions

### 2017-11-14 inst/suppFigure2d_lnc34aCage/lnc34aCAGE.Rmd
renamed all inst directories, corresponding data-raw files, and updated Rmd input path

dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
url <- "lnc34aCAGE.rds"
cage <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    arrange(desc(level)) %>%
    mutate(y = 1:length(pull(., level)))

>>>>

dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
url <- "suppFigure2d_lnc34aCage.rds"
cage <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    arrange(desc(level)) %>%
    mutate(y = 1:length(pull(., level)))

### 2017-11-14 inst/suppFigure2e_lnc34aSplJnc/lnc34aSplJnc.Rmd
renamed all inst directories, corresponding data-raw files, and updated Rmd input path

#splice junctions
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
url <- "lnc34aSpliceJncs.rds"
splJnc <- read_rds(gzcon(url(file.path(dataUrl, url))))

>>>>

#splice junctions
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
url <- "suppFigure2e_lnc34aSplJnc.rds"
splJnc <- read_rds(gzcon(url(file.path(dataUrl, url))))
